Interactive Markdown to explore Clustering

### 2017-04-06 src/ClusterComparison.Rmd
Major formatting changes

renderTable({
    clust <- clustering()
    x <- table(clust$cluster,pD$Condition)
    out <- data.frame("Cluster"=rownames(x),
	       "Virgin"=unname(x[,"V"]),
	       "Pregnant"=unname(x[,"P"]),
	       "Lactation"=unname(x[,"L"]),
	       "Involution"=unname(x[,"I"]))
})

>>>>

renderTable({
    clust <- clustering()
    x <- table(clust$cluster,pD$Condition)
    out <- data.frame("Cluster"=rownames(x),
	       "Virgin"=unname(x[,"NP"]),
	       "Pregnant"=unname(x[,"G"]),
	       "Lactation"=unname(x[,"L"]),
	       "Involution"=unname(x[,"PI"]))
})
